%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Software Engineer \& Security Researcher } % Job title
{Freelance} % Organization
{Online} % Location
{2024 - 2024} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item { While researching WIN32 api and Windows Defender mechanisms, I implemented my own hardware ID in pure C, which is not detected by any antivirus.  }
\end{cvitems}
}

%------------------------------------------------    


%------------------------------------------------

\cventry
{Python Software Engineer} % Job title
{Freelance} % Organization
{Online} % Location
{Dec. 2019 - 2021} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item { This is the beginning of my career as a programmer. I developed scrappers for different platforms, created bots (Telegram, Discord, Bridged) and simple services. }
\end{cvitems}
}

%------------------------------------------------

\cventry
{Software (Web3, Python) Engineer} % Job title
{Freelance} % Organization
{Online} % Location
{Dec. 2022 - 2022} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item { Working for another startup, I was developing an analog of tradingview (collecting a huge stream of data from different exchanges using a parser) into kafka, and then running various strategies in containers (my devops then put k8s)  } 
\end{cvitems}
}

%------------------------------------------------

\cventry
{Software (Go) Engineer} % Job title
{Freelance} % Organization
{Online} % Location
{Dec. 2022 - 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item { Working for myself, actively used Golang during this time. Especially embraced the use of microservices. Mostly rewrote old constructs from Python. Accelerated, checked metrics, redesigned tests, etc.  } 
\end{cvitems}
}

%------------------------------------------------

\cventry
{Web3 (Go, JS, Python, Solidity) Engineer} % Job title
{Freelance} % Organization
{Online} % Location
{Dec. 2022 - 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item { Since that time, I have periodically taken on web3 development. I mostly wrote blockchain parsers, sometimes my own contracts, sometimes set up nodes, created arbitrage bots and studied economics.  } 
\end{cvitems}
}

%------------------------------------------------

\cventry
{JS Security Researcher } % Job title
{Freelance} % Organization
{Online} % Location
{Dec. 2021 - 2021} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item { Interesting research. I bypassed AKAMAI's bot protection algorithms by accurately deobfuscating code and understanding what's under the hood. This allowed us to automate many services using this (very popular) strong protection.  }
\end{cvitems}
}

%------------------------------------------------

\cventry
{JS/Cloudflare Security Researcher } % Job title
{Freelance} % Organization
{Online} % Location
{Dec. 2021 - 2021} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item { Another one of my researchs. I bypassed cloudflare's bot protection for WEBSOCKETS/HTTP requests, which allows us to automate culling from HUGE sites. } 
\end{cvitems}
}

%------------------------------------------------

\cventry
{Fullstack (Web3/Python) Backend Engineer} % Job title
{AIDLT BY} % Organization
{Republic of Belarus, Minsk} % Location
{Nov. 2021 - Apr. 2022} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item { While working for a startup, I did (later in a lead position) game development on a web3 platform. 
Also, creating bot bridges for different messengers. }
\end{cvitems}
}

%------------------------------------------------

\cventry
{Backend Lead Engineer} % Job title
{Freelance} % Organization
{Online} % Location
{2023 - 2024} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item{ During this period, I focused on a few particularly large projects where I took on a lead role.} 
\item { I brought up a large service for receiving sms from unstable providers, ensuring reliability and timeliness for the end user (95th percentile) by setting up the entire infrastructure myself. And then I wrote another service for this service, which also aggregates multiple providers and creates bot farms. }
\item {Each project implemented its own hashing algorithms, queues, etc., and used Prometheus and Grafana metrics.  }
\end{cvitems} 
}


%------------------------------------------------

\end{cventries}